Instructions for ACL 2019 Proceedings

### 2023-12-09 paper/paper.tex
further paper contribution

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2019}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amssymb}

@@

Grammatical cases are a system of marking nouns and noun modifiers in order
to indicate the noun (modifier)'s intended grammatical function in a sentence.
While historically English had grammatical cases, they survive in modern English
only in pronouns. Every pronoun in English has three different forms representing
three different cases. These are:

@@

Russian, being a member of the Slavic branch of the Indo-European languages,
has a fully functioning grammatical case system applying for all nouns
unlike English. Nouns and noun modifiers in Russian inflect for case
by changing the ending of the word, and the exact manner by which an ending
changes depends on the ending, case, and number of the noun.

Table 1 shows the different endings of the Russian nominative and
genitive cases in the singular and plural.

\begin{table}[t!]
\begin{center}
\begin{tabular}{|l|l|l}
\hline & \textbf{Singular} & \textbf{Plural} \\ \hline
\textbf{Nominative} & -a, -ja, -ija & -y, -i, -ii \\
\textbf{Genitive} & -y, -i, -ii & $\varnothing$, -', -ij \\ \hline
\textbf{Nominative} & $\varnothing$, -'/j, -ij & -y, -i, -ii, -je \\
\textbf{Genitive} & -a, -ja, -ija & -ov, -jej/jev, -ijev \\ \hline
\textbf{Nominative} & -o, -je & -a, -ja \\
\textbf{Genitive} & -a, -ja & $\varnothing$, -j, -jej \\ \hline
\textbf{Nominative} & -' & -i \\
\textbf{Genitive} & -i & -jej \\ \hline
\textbf{Nominative} & -mja & -mjena \\
\textbf{Genitive} & -mjeni & -mjon \\ \hline
\end{tabular}
\end{center}
\caption{\label{declension} Nominative and genitive endings for nouns with different endings. Note that the apostrophe ' is a palatalization character, corresponding to \foreignlanguage{russian}{ь} in Cyrillic. }
\end{table}

\section{General Instructions}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, authors' names and complete
addresses, which must be centered at the top of the first page, and
any full-width figures or tables (see the guidelines in
Subsection~\ref{ssec:first}). \textbf{Type single-spaced.}  Start all
pages directly under the top margin. See the guidelines later
regarding formatting the first page.  The manuscript should be
printed single-sided and its length
should not exceed the maximum page limit described in Section~\ref{sec:length}.
Pages are numbered for  initial submission. However, \textbf{do not number the pages in the camera-ready version}.

By uncommenting {\small\verb|\aclfinalcopy|} at the top of this 
 document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.  When you first create your submission on softconf, please fill in your submitted paper ID where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top.

The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.  The ACL 2019 \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\aclfinalcopy|} is commented out.

\subsection{The Ruler}
The ACL 2019 style defines a printed ruler which should be presented in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document without the provided
style files, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment the {\small\verb|\aclfinalcopy|} command in the document preamble.)

Reviewers: note that the ruler measurements do not align well with
lines in the paper -- this turns out to be very difficult to do well
when the paper contains many figures and equations, and, when done,
looks ugly. In most cases one would expect that the approximate
location will be adequate, although you can also use fractional
references (\emph{e.g.}, the first paragraph on this page ends at mark $108.5$).

\subsection{Electronically-available resources}

ACL provides this description in \LaTeX2e{} (\texttt{\small acl2019.tex}) and PDF
format (\texttt{\small acl2019.pdf}), along with the \LaTeX2e{} style file used to
format it (\texttt{\small acl2019.sty}) and an ACL bibliography style (\texttt{\small acl\_natbib.bst})
and example bibliography (\texttt{\small acl2019.bib}).
These files are all available at
\texttt{\small http://acl2019.org/downloads/ acl2019-latex.zip}. 
 We
strongly recommend the use of these style files, which have been
appropriately tailored for the ACL 2019 proceedings.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). PDF files are usually produced from
\LaTeX\ using the \textit{pdflatex} command. If your version of
\LaTeX\ produces Postscript files, you can convert these into PDF
using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
Adobe Distiller to generate PDF.

Please make sure that your PDF file includes all the necessary fonts
(especially tree diagrams, symbols, and fonts with Asian
characters). When you print or create the PDF file, there is usually
an option in your printer setup to include none, all or just
non-standard fonts.  Please make sure that you select the option of
including ALL the fonts. \textbf{Before sending it, test your PDF by
  printing it from a computer different from the one where it was
  created.} Moreover, some word processors may generate very large PDF
files, where each page is rendered as an image. Such images may
reproduce poorly. In this case, try alternative ways to obtain the
PDF. One way on some systems is to install a driver for a postscript
printer, send your document to the printer specifying ``Output to a
file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm
x 29.7 cm) when formatting the paper. When working with
\texttt{dvips}, for instance, one should specify \texttt{-t a4}.
Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
preamble (directly below the \verb|\usepackage| commands). Then using 
\texttt{dvipdf} and/or \texttt{pdflatex} which would make it easier for some.

Print-outs of the PDF file on A4 paper should be identical to the
hardcopy version. If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on A4
paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
 If you cannot meet the above requirements about the production of 
 your electronic submission, please contact the publication chairs 
 above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's \textbf{Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use \textbf{Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[t!]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
subsection titles & 11 pt & bold \\
document text & 11 pt  &\\
captions & 10 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns. Do not use footnotes for affiliations. Do not include the
paper ID number assigned during the submission process. Use the
two-column format only when you begin the abstract.

\textbf{Title}: Place the title centered at the top of the first page, in
a 15-point bold font. (For a complete guide to font sizes and styles,
see Table~\ref{font-table}) Long titles should be typed on two lines
without a blank line intervening. Approximately, put the title at 2.5
cm from the top of the page, followed by a blank line, then the
author's names(s), and the affiliation on the following line. Do not
use only initials for given names (middle initials are allowed). Do
not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not
``MITCHELL'').  Do not format title and section headings in all
capitals as well except for proper names (such as ``BLEU'') that are
conventionally in all capitals.  The affiliation should contain the
author's complete address, and if possible, an electronic mail
address. Start the body of the first page 7.5 cm from the top of the
page.

The title, author names and addresses should be completely identical
to those entered to the electronical paper submission website in order
to maintain the consistency of author information among all
publications of the conference. If they are different, the publication
chairs may resolve the difference without consulting with you; so it
is in your own interest to double-check that the information is
consistent.

\textbf{Abstract}: Type the abstract at the beginning of the first
column. The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.6 cm on each side. Center the word \textbf{Abstract} in a 12 point bold
font above the body of the abstract. The abstract should be a concise
summary of the general thesis and conclusions of the paper. It should
be no longer than 200 words. The abstract text should be in 10 point font.

\textbf{Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in the present document. Do not include page numbers.

\textbf{Indent}: Indent when starting a new paragraph, about 0.4 cm. Use 11 points for text and subsection headings, 12 points for section headings and 15 points for the title.

\begin{table}
\centering
\small
\begin{tabular}{cc}
\begin{tabular}{|l|l|}
\hline
\textbf{Command} & \textbf{Output}\\\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular} & 
\begin{tabular}{|l|l|}
\hline
\textbf{Command} & \textbf{Output}\\\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\\hline
\end{tabular}
\end{tabular}
\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\subsection{Sections}

\textbf{Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals.
Do not number subsubsections.

\begin{table*}[t!]
\centering
\begin{tabular}{lll}
  output & natbib & previous ACL style files\\
  \hline
  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
\end{tabular}
\caption{Citation commands supported by the style file.
  The citation style is based on the natbib package and
  supports all natbib citation commands.
  It also supports commands defined in previous ACL style files
  for compatibility.
  }
\end{table*}

@@

We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\citet| (cite in text)
to get ``author (year)'' citations.

You can use the command \verb|\citealp| (alternative cite without 
parentheses) to get ``author year'' citations (which is useful for 
using citations within parentheses, as in \citealp{Gusfield:97}).

If the Bib\TeX{} file contains DOI fields, the paper
title in the references section will appear as a hyperlink
to the DOI, using the hyperref \LaTeX{} package.
To disable the hyperref package, load the style file
with the \verb|nohyperref| option: \\{\small
\verb|\usepackage[nohyperref]{acl2019}|}

\textbf{Compilation Issues}: Some of you might encounter the following error during compilation:

``{\em \verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.}''

This happens when \verb|pdflatex| is used and a citation splits across a page boundary. To fix this, the style file contains a patch consisting of the following two lines: (1) \verb|\RequirePackage{etoolbox}| (line 454 in \texttt{acl2019.sty}), and (2) A long line below (line 455 in \texttt{acl2019.sty}).

If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \verb|hyperref| package (see above), recompile and see the problematic citation.
Next rewrite that sentence containing the citation. (See, {\em e.g.}, {\small\tt http://tug.org/errors.html})

\textbf{Digital Object Identifiers}:  As part of our work to make ACL
materials more widely used and cited outside of our discipline, ACL
has registered as a CrossRef member, as a registrant of Digital Object
Identifiers (DOIs), the standard for registering permanent URNs for
referencing scholarly materials.  As of 2017, we are requiring all
camera-ready references to contain the appropriate DOIs (or as a
second resort, the hyperlinked ACL Anthology Identifier) to all cited
works.  Thus, please ensure that you use Bib\TeX\ records that contain
DOI or URLs for any of the ACL materials that you reference.
Appropriate records should be found for most materials in the current
ACL Anthology at \url{http://aclanthology.info/}.

As examples, we cite \cite{P16-1001} to show you how papers with a DOI
will appear in the bibliography.  We cite \cite{C14-1001} to show how
papers without a DOI but with an ACL Anthology Identifier will appear
in the bibliography.

As reviewing will be double-blind, the submitted version of the papers
should not include the authors' names and affiliations. Furthermore,
self-references that reveal the author's identity, \emph{e.g.},
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''  
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper. ACL 2019 reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.

\textbf{Please do not use anonymous citations} and do not include
 when submitting your papers. Papers that do not
conform to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading \textbf{References}; place the section before any Appendices. 
Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
By using a .bib file, as in this template, this will be automatically 
handled for you. See the \verb|\bibliography| commands near the end for more.

Provide as complete a citation as possible, using a consistent format,
such as the one for \emph{Computational Linguistics\/} or the one in the 
\emph{Publication Manual of the American 
Psychological Association\/}~\cite{APA:83}. Use of full names for
authors rather than initials is preferred. A list of abbreviations
for common computer science journals can be found in the ACM 
\emph{Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations, 
short citations and multiple citations as described above.

\begin{itemize}
\item Example citing an arxiv paper: \cite{rasooli-tetrault-2015}. 
\item Example article in journal citation: \cite{Ando2005}.
\item Example article in proceedings, with location: \cite{borsch2011}.
\item Example article in proceedings, without location: \cite{andrew2007scalable}.
\end{itemize}
See corresponding .bib file for further details.

Submissions should accurately reference prior and related work, including code and data. If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced. If multiple versions of a piece of prior work exist, the one used by the authors should be referenced. Authors should not rely on automated citation indices to provide accurate references for prior and related work.

\textbf{Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: \textbf{Appendix A. Title of Appendix}.

\subsection{Footnotes}

\textbf{Footnotes}: Put footnotes at the bottom of the page and use 9
point font. They may be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the line
separating the footnotes from the text.}

\subsection{Graphics}

\textbf{Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns.  Color
illustrations are discouraged, unless you have verified that  
they will be understandable when printed in black ink.

\textbf{Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and 
tables below the body, using 10 point text. Captions should be placed below illustrations. Captions that are one line are centered (see Table~\ref{font-table}). Captions longer than one line are left-aligned (see Table~\ref{tab:accents}). Do not overwrite the default caption sizes. The acl2019.sty file is compatible with the caption and subcaption packages; do not add optional arguments.

\subsection{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate people who are color-blind (as well as those printing
to paper), grayscale readability for all accepted papers will be
encouraged.  Color is not forbidden, but authors should ensure that
tables and figures do not rely solely on color to convey critical
distinctions. A simple criterion: All curves and points in your figures should be clearly distinguishable without color.

% Min: no longer used as of ACL 2018, following ACL exec's decision to
% remove this extra workflow that was not executed much.
% BEGIN: remove
%% \section{XML conversion and supported \LaTeX\ packages}

%% Following ACL 2014 we will also we will attempt to automatically convert 
%% your \LaTeX\ source files to publish papers in machine-readable 
%% XML with semantic markup in the ACL Anthology, in addition to the 
%% traditional PDF format.  This will allow us to create, over the next 
%% few years, a growing corpus of scientific text for our own future research, 
%% and picks up on recent initiatives on converting ACL papers from earlier 
%% years to XML.

%% We encourage you to submit a ZIP file of your \LaTeX\ sources along
%% with the camera-ready version of your paper. We will then convert them
%% to XML automatically, using the LaTeXML tool
%% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
%% a number of \LaTeX\ packages, including the ACL 2018 stylefile. These
%% bindings allow LaTeXML to render the commands from these packages
%% correctly in XML. For best results, we encourage you to use the
%% packages that are officially supported by LaTeXML, listed at
%% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
% END: remove

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section{Length of Submission}
\label{sec:length}

The ACL 2019 main conference accepts submissions of long papers and
short papers.
 Long papers may consist of up to eight (8) pages of
content plus unlimited pages for references. Upon acceptance, final
versions of long papers will be given one additional page -- up to nine (9)
pages of content plus unlimited pages for references -- so that reviewers' comments
can be taken into account. Short papers may consist of up to four (4)
pages of content, plus unlimited pages for references. Upon
acceptance, short papers will be given five (5) pages in the
proceedings and unlimited pages for references. 
For both long and short papers, all illustrations and tables that are part
of the main text must be accommodated within these page limits, observing
the formatting instructions given in the present document. Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.

ACL 2019 does encourage the submission of additional material that is relevant to the reviewers but not an integral part of the paper. There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.  Do not include this additional material in the same document as your main paper. Additional material must be submitted as one or more separate files, and must adhere to the same anonymity guidelines as the main paper. The paper must be self-contained: it is optional for reviewers to look at the supplementary material. Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers. Refer to Appendix~\ref{sec:appendix} and Appendix~\ref{sec:supplemental} for further information.

Workshop chairs may have different rules for allowed length and
whether supplemental material is welcome. As always, the respective
call for papers is the authoritative source.

@@

\section{Supplemental Material}
\label{sec:supplemental}
Submissions may include non-readable supplementary material used in the work and described in the paper. Any accompanying software and/or data should include licenses and documentation of research review as appropriate. Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper. Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather
than central) to the paper. \textbf{Submissions that misuse the supplementary 
material may be rejected without review.}
Supplementary material may include explanations or details
of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system,
pseudo-code or source code, and data. (Source code and data should
be separate uploads, rather than part of the paper).

The paper should not rely on the supplementary material: while the paper
may refer to and cite the supplementary material and the supplementary material will be available to the
reviewers, they will not be asked to review the
supplementary material.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2019}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{tipa}

@@

Grammatical cases are a system of marking nouns and noun modifiers in order
to indicate the noun (modifier)'s intended grammatical function in a sentence.
While historically English had grammatical cases, they survive in modern English
only through pronouns. Every pronoun in English has three different forms representing
three different cases. These are:

@@

Russian, being a member of the Slavic branch of the Indo-European languages,
has a fully functioning grammatical case system which is used for all nouns
unlike English. Nouns and noun modifiers in Russian inflect for case
by changing the ending of the word, and the exact manner by which an ending
changes depends on the ending, case, and number of the noun. Table 1 shows 
the different possible endings of the Russian nominative and genitive cases in 
the singular and plural.

There are, of course, various irregularities in forming the genitive case
for certain nouns. Some nouns have suppletive roots, found only in the
plural form: for example, the noun \emph{\v{c}elovjek} (person) has the regular singular 
genitive form \emph{\v{c}elovjeka}. However, in the nominative plural, it becomes
\emph{ljudji}, and in the genitive plural \emph{ljudjej}, using an entirely different
noun stem for the plural cases.

The reason we chose the genitive case to study is because its formation,
much like the English past tense, is fairly regular in the singular; in a majority of cases,
the genitive form can be simply derived from the nominative by modifying the
noun's ending based on the table. We also chose it because the genitive plural,
in particular, tends to be more irregular. It is often the aspect of Russian
that is most difficult for learners of the language to comprehend, so
we wanted to investigate how a gradient-descent neural network would handle
acquiring the genitive case in singular and plural forms.

We also chose the genitive because it is a case that (with the exception of
indeclinable nouns, which we ignored for this paper) always changes the noun
in some way. This is contrasted with the accusative case, which can either
not change the noun, use the genitive form to represent the accusative, or 
use its own unique endings. Whichever scenario applies depends on not just 
the ending of the noun, but also its gender and animacy.

\begin{table}[t!]
\begin{center}
\begin{tabular}{|l|l|l}
\hline & \textbf{Singular} & \textbf{Plural} \\ \hline
\textbf{Nominative} & -a, -ja, -ija & -I\textbackslash, -i, -ii \\
\textbf{Genitive} & -I\textbackslash, -i, -ii & $\varnothing$, -', -ij \\ \hline
\textbf{Nominative} & $\varnothing$, -'/j, -ij & -I\textbackslash, -i, -ii, -je \\
\textbf{Genitive} & -a, -ja, -ija & -ov, -jej/jev, -ijev \\ \hline
\textbf{Nominative} & -o, -je & -a, -ja \\
\textbf{Genitive} & -a, -ja & $\varnothing$, -j, -jej \\ \hline
\textbf{Nominative} & -' & -i \\
\textbf{Genitive} & -i & -jej \\ \hline
\textbf{Nominative} & -mja & -mjena \\
\textbf{Genitive} & -mjeni & -mjon \\ \hline
\end{tabular}
\end{center}
\caption{\label{declension} Nominative and genitive endings for nouns with different endings, written with X-SAMPA. Note that the apostrophe ' is a palatalization character, corresponding to \foreignlanguage{russian}{ь} in Cyrillic. }
\end{table}

\section{Featural representation of Russian phonemes}

Rumelhart and McClelland (1986) made use of a scheme to encode
English phoneme units, known as Wickelphones and Wickelfeatures, described
in Wickelgren (1969). Wickelphones are phoneme units representing
each phone in a word as triples, which consist of the phoneme itself,
its predecessor to the left, and its successor on the right.
Wickelfeatures are a means of representing Wickelphones as distributed
patterns of activation by capturing one feature of the central phoneme,
one feature of the predecessor, and one feature of the successor.

The feature coding scheme we used to capture Russian phonemes did not
differ heavily from Rumelhart and McClelland's scheme. However, in order
to accomodate Russian's richer consonant inventory, we had to add an
extra dimension to the scheme to account for plain vs. palatalized
consonants, the latter of which are in abundance in Russian phonology.

In addition to accomodating Russian phonology for Wickelfeatures, we had to make some
decisions regards to what exact sounds are in Russian. Specifically,
the status of the close central unrounded vowel \textipa{/\textbari/} 
(written in Cyrillic as \foreignlanguage{russian}{ы}) as a separate 
vowel morpheme in Russian is a subject of heavy debate. Some linguists 
believe in a five-vowel analysis, meaning that the vowel \textipa{/\textbari/} 
is in complementary distribution with the close front unrounded vowel 
\textipa{/i/} (written in Cyrillic as \foreignlanguage{russian}{и}), 
such that the vowel phoneme \textipa{/i/} occurs after soft (i.e. 
palatalized) consonants, whereas the vowel phoneme \textipa{/\textbari/} 
occurs after hard (i.e. plain) consonants. Other linguists believe in a
six-vowel analysis, asserting \textipa{/\textbari/} as a separate phoneme.

Another set of phonemes with disputed status in Russian are palatalized
velar consonants (i.e. \textipa{/k\super j/}, \textipa{/g\super j/}, 
and \textipa{/x\super j/}) as well as the palatalized voiceless alveolar
sibilant affricate \textipa{/\t{ts}\super j/}. In most cases, the velar consonants
become soft when followed by front vowels (except in the case of a word
boundary between the consonant and vowel), and the affricate is generally
always hard. It is only in certain loanwords and foreign names that
the consonants may become palatalized in other contexts.

For the sake of our experiment, however, we have chosen to follow the
five-vowel analysis and not count the extra palatalized consonants
as Russian phonemes. The phonemic status of the vowel \textipa{/\textbari/}
is marginal, only occuring isolated in the verb \foreignlanguage{russian}{ыкать}
(to pronounce the sound \foreignlanguage{russian}{ы}) and in borrowed names
of places in Russia. By following the five-vowel analysis, we can account for
one less vowel, because \textipa{/\textbari/} and \textipa{/i/} are otherwise
in complementary distribution in all other environments. Likewise, because
the velar consonants are normally only palatalized following front vowels,
there is no need to account for such redundant information.

Table 2 shows the scheme that we used to categorize Russian phonemes
on five simple dimensions.

\begin{table*}[t!]
\centering
\begin{tabular}{cccccccccccccc}
    \multicolumn{2}{c}{} & \multicolumn{12}{c}{Place}\\\hline
    \multicolumn{2}{c}{} & \multicolumn{4}{c}{Front} & \multicolumn{4}{c}{Middle} & \multicolumn{4}{c}{Back}\\\hline
    \multicolumn{2}{c}{} & \multicolumn{2}{c}{Voiceless} & \multicolumn{2}{c}{Voiced} & \multicolumn{2}{c}{Voiceless} & \multicolumn{2}{c}{Voiced} & \multicolumn{2}{c}{Voiceless} & \multicolumn{2}{c}{Voiced}\\\hline
    \multicolumn{2}{c}{} & H & S & H & S & H & S & H & S & H & S & H & S\\\hline
    \multirow{2}{50px}{Interrupted} & Stop & p & p' & b & b' & t & t' & d & d' & k & - & g & -\\
    & Nasal & - & - & m & m' & - & - & n & n' & - & - & - & - \\
    \multirow{2}{50px}{Cont.Cons.} & Fricative & f & f' & v & v' & s & s' & z & z' & s\` & t\_s\textbackslash & z\` & -\\
                                        & Liq/Sem. & - & - & l & l' & t\_s & - & r & r' & x & - & - & j\\
    \multirow{2}{50px}{Vowel} & Close & - & - & i & - & - & - & - & - & - & - & u & -\\
                              & Open & - & - & e & - & - & - & a & - & - & - & o & -\\
\end{tabular}
\caption{Categorization of Russian phonemes on five dimensions.
All phonemes are written using X-SAMPA.}
\end{table*}

\section{Experimental setup}

To run our experiment, we first obtained a Russian word list, filtered the
word data, then preprocessed the data into a format that can be used by a
neural network model. We then trained our neural network models based on
our word data and evaluated the results. The procedure for these steps
is outlined in the subsections below.

\subsection{Collecting Russian nouns and declensions}

In order to train the neural network, we needed a list of Russian nouns
and their genitive singular and plural forms. For this, we scraped words
from Wiktionary. Wiktionary is an online, multilingual, and free project
to create a dictionary for all natural languages. These dictionary entries
often contain additional information about words in languages, such as verb
conjugations, example sentences, synonyms and antonyms, and most importantly,
noun declensions.

Every Russian noun with an entry on Wiktionary is accessible through the category
page \textbf{Category:Russian Nouns}. Using Wiktionary's MediaWiki API, we gathered
every noun in this category in batches of 500 (due to API limitations). For each
batch, we checked to make sure that the word only contained letters in the modern
Russian Cyrillic alphabet, because Wiktionary also has entries for Russian words
containing characters from different alphabets (e.g. \textbf{\foreignlanguage{russian}{QR-код}},
meaning ``QR code'') as well as alternate spellings of words containing archaic letters 
unused since the Russian spelling reform of 1918.

After performing this initial pruning, we then queried the API for each word's
entry in Wiktionary and attempted to extract its genitive singular and plural
forms from the declension table available in the entry. If either the singular
or plural genitive forms were missing from the table, the noun is discarded.
This can happen if a word is an indeclinable loanword or only exists in either
the singular or plural forms. We then save the word, its genitive singular and
plural forms into a wordlist, which will be consulted during the pre-processing
and training phases.

\subsection{Noun data pre-processing}

Before the noun data can be used as input to train the neural network, it must
first be converted into a representation usable by the model.

The first transformation that takes place is converting the noun forms'
Russian Cyrillic representation into a phonemic representation in X-SAMPA\@.
Because the Russian alphabet is much more phonemically consistent than English,
meaning it is possible to derive a word's phonemic representation by iterating
through its Cyrillic representation one letter at a time.

% TODO: explain this better
After being converted into X-SAMPA, each phoneme would then be converted into
its Wickelphone/Wickelfeature representations.

The Wickelfeatures would then be converted into arrays of activations for
certain features.

\subsection{Neural network}

The basis of our neural network is a gradient-descent neural network powered by the
\emph{PyTorch} library. It uses a single linear transformation layer with the
input size being the number of Wickelfeatures that can be activated for,
and the output size being either 1 or 2 times the number of Wickelfeatures
that can be activated for, depending on whether the model is one of the
two smaller models learning individual genitive cases or the larger model
learning both genitive cases.

@@

@@
